\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2020-11-01 paper.tex
Updates from Overleaf

The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next

>>>>

The software pipeline is built of multiple executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor.
